MSTK: Mesh Toolkit, v 1.83

### 2011-11-21 docs/MSTK.tex
Forgot to update version number to 1.8
Modified the arguments for MSTK_Mesh_Distribute and MSTK_Mesh_Read_Distribute

\title{MSTK: Mesh Toolkit, v 1.7}

@@

\item[] {\bf {\em int} MSTK\_Mesh\_Read\_Distribute({\em Mesh\_ptr
      *}recv\_mesh, {\em const char*} global\_mesh\_name, {\em int} dim,
    {\em int} ring, {\em int} with\_attr, {\em int} rank, {\em int}
    num, {\em MPI\_Comm} comm)}: Routine reads a mesh of dimension
  'dim' from file 'global\_mesh\_name' on processor 'rank' and
  distributes it 'num' processors. 'comm' is the communicator to be
  used by MPI. If 'ring' is 0, there is no overlap of the highest
  level entities between processors - only entities on processor
  boundaries will be duplicated on other processors. If 'ring' is N,
  then 'N' layers of the highest level entities will overlap between
  processors ({\em Currently, only 1 layer of overlap elements are
    supported}). If 'with\_attr' is 1, then MSTK sets up the links
  necessary to synchronize attribute data across processors. This routine must be called from only one processor.

\item[] {\bf {\em int} MSTK\_Mesh\_Distribute({\em Mesh\_ptr
      *}recv\_mesh, {\em int} ring, {\em int} with\_attr, {\em int}
    rank, {\em int} num, {\em MPI\_Comm} comm)}: Similar to the above
  Read\_Distribute routine except that it does do any read. On the
  processor, that is doing the distributing, recv\_mesh holds the
  input and out meshes.

>>>>

\title{MSTK: Mesh Toolkit, v 1.83}

@@

\item[] {\bf {\em int} MSTK\_Mesh\_Read\_Distribute({\em Mesh\_ptr
      *}recv\_mesh, {\em const char*} global\_mesh\_name, {\em int} *dim,
    {\em int} ring, {\em int} with\_attr, {\em int} rank, {\em int}
    num, {\em MPI\_Comm} comm)}: Routine reads a mesh of dimension
  'dim' from file 'global\_mesh\_name' on processor 'rank' and
  distributes it 'num' processors. 'comm' is the communicator to be
  used by MPI. If 'ring' is 0, there is no overlap of the highest
  level entities between processors - only entities on processor
  boundaries will be duplicated on other processors. If 'ring' is N,
  then 'N' layers of the highest level entities will overlap between
  processors ({\em Currently, only 1 layer of overlap elements are
    supported}). If 'with\_attr' is 1, then MSTK sets up the links
  necessary to synchronize attribute data across processors. This routine must be called from only one processor.

\item[] {\bf {\em int} MSTK\_Mesh\_Distribute({\em Mesh\_ptr
      *}recv\_mesh, {\em int} *dim, {\em int} ring, {\em int}
    with\_attr, {\em int} rank, {\em int} num, {\em MPI\_Comm} comm)}:
  Similar to the above Read\_Distribute routine except that it does
  not do any read. On the root processor, 'recv\_mesh' is an
  input-output parameter - the application uses it to send in the full
  mesh to be distributed and the mesh partition belonging to the root
  processor is returned in it. On other processors, this is an output
  parameter only. Also, 'dim', indicating the topological dimension of
  the input mesh, is an input parameter on the root processor while it
  is an output parameter on the other processors.
